\thesistitle

### 2019-08-21 sections/introduction.tex
Okay this was the last of the introduction
#introduction #waytoomuchtimespent #yolo #thisisgonnagetmeintrouble #deadlinetomorrow #stress #help

\chapter{Introduction}
%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economic challenges.
%Problem Analysis: Here you present your analysis of the problem situation that your research will address.
%How does this problem manifest itself at your host organization?
%Also summarises existing scientific insight into the problem.}
\label{ch:introduction}
Refactoring is the process of restructuring code to improve quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality. Many methods have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}. However, most of these methods still require a manual assessment of where and when to apply them. Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}. %For a large part, refactoring requires domain knowledge to do it right. However, there are also refactoring opportunities that are rather trivial and repetitive to execute. In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

Duplication in source code is often seen as one of the most harmful types of technical debt. If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}. Additionally, the codebase size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.

\todo{A paragraph about current clone types being ill-defined for automated refactoring}

In this study, we use refactoring techniques to automatically reduce duplication in software systems. This allows us to obtain before- and after-refactoring snapshots of software systems. We use software maintainability metrics to measure the impact of refactoring clones. We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones. Furthermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.

@@

The process of improving maintainability through the refactoring of duplicate code is time-consuming and error-prone. This process mainly consists of two aspects:
\begin{itemize}
	\item Find refactoring candidates, either tool-assisted or fully manually.
	\item Refactor identified candidates, either tool-assisted or fully manually.
\end{itemize}
Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally span for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}. Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation}, leading to a potentially non-optimal selection of clones that are presented to the developer.

>>>>

\chapter{Introduction}
%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economic challenges.
%Problem Analysis: Here you present your analysis of the problem situation that your research will address.
%How does this problem manifest itself at your host organization?
%Also summarises existing scientific insight into the problem.}
\label{ch:introduction}
Refactoring is the process of restructuring code to improve quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality. Many methods have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}. However, most of these methods still require a manual assessment of where and when to apply them. Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, does not happen at all \cite{mens2003refactoring}, or leaves unintentional side-effects in the code \cite{bavota2012does}. %For a large part, refactoring requires domain knowledge to do it right. However, there are also refactoring opportunities that are rather trivial and repetitive to execute. In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

Duplication in source code, also known as ``code clones'', is often seen as one of the most harmful types of technical debt. If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}. Additionally, the codebase size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.

Automating the refactoring process of code clones can help to deal with duplication problems. It can also assist in the evaluating whether refactoring a specific clone would improve the codebase, by using established metrics \cite{heitlager2007practical} to determine whether the code after applying the refactoring has improved. Howeverm clones detected on basis of established clone definitions \cite{roy2007survey} may not always be suitable for automated refactoring.

In this study, we define clones such that they can be automatically refactored and build a tool to automatically refactor such clones. This allows us to obtain before- and after-refactoring snapshots of software systems. We use software maintainability metrics to measure the impact of these refactorings. We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones. Furthermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.

@@

The process of improving maintainability through the refactoring of duplicate code is time-consuming and error-prone. This process mainly consists of two aspects:
\begin{itemize}
	\item Find refactoring candidates, either tool-assisted or fully manually.
	\item Refactor identified candidates, either tool-assisted or fully manually.
\end{itemize}
Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally span for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}. Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data \ref{alves2010deriving}. These methods do not always accurately reflect the effect of refactoring the system, leading to a potentially non-optimal selection of clones that are presented to the developer.
